\documentclass[12pt]{article}

%% Define some new colors
\usepackage{xcolor}
\definecolor{mBlue}{RGB}{51, 77, 167}
\newcommand{\blue}[1]{{\color{mBlue}#1}}

%% Page and text formatting
\usepackage[left=1.0in, right=1.0in, top=1.0in, bottom=1.0in]{geometry} % margins
\usepackage{setspace}
\singlespacing % No more than 6 lines of text per inch
\usepackage{amsmath, amsfonts}
\usepackage[T1]{fontenc}
\usepackage{times}

%% Make the sections start with (a), (b), etc.
\renewcommand\thesection{(\alph{section})}
\renewcommand\thesubsection{(\alph{subsection})}

%% Set up footer
\usepackage{fancyhdr}
\fancypagestyle{CVfooter}
{
 \lhead{}
 \chead{}
 \rhead{}
 \lfoot{\small{Thanh Dat Vu}}
 \cfoot{\small{\today}}
 \rfoot{\small{\thepage/2}}
 \renewcommand{\headrulewidth}{0.0pt}
 \renewcommand{\footrulewidth}{0.5pt}
}

%% Set up hyperlinks
\usepackage[linktoc=page]{hyperref}
\hypersetup{
  colorlinks = true,
  urlcolor = mBlue,
  citecolor = mBlue,
  linkcolor = mBlue,
}

%% Set up citations and bibliography
\usepackage{bibunits}
\usepackage[sort&compress,super]{natbib}
\defaultbibliographystyle{apsrev4-2}
\setcitestyle{comma}
\setlength{\bibsep}{0pt}
\renewcommand{\bibnumfmt}[1]{\ \ \ #1.}
\renewcommand\refname{\vspace{-7mm}}

%% This allows us to start a bibliography with arbitrary number
\usepackage{etoolbox}
\makeatletter
\newcommand*{\newbibstartnumber}[1]{%
  \apptocmd{\thebibliography}{%
    \global\c@NAT@ctr #1\relax
    \addtocounter{NAT@ctr}{-1}%
  }{}{}%
}
\makeatother

%% Reduce whitespace around lists (globally)
\usepackage{enumitem}
\setlist[itemize]{nosep,left=0pt}
\setlist[enumerate]{nosep}
\setlist[description]{nosep}

%% Formatting for sections
\usepackage[compact]{titlesec}
\titleformat*{\section}{\normalsize\bfseries}
\titlespacing*{\section}{0mm}{2mm}{1mm}[0mm] % left top bottom right
\titleformat*{\subsection}{\normalsize\bfseries}
\titlespacing*{\subsection}{0mm}{2mm}{1mm}[0mm]
\titleformat*{\subsubsection}{\normalsize\bfseries\itshape}
\titlespacing*{\subsubsection}{0mm}{1mm}{0mm}[0mm]

\begin{document}
\pagestyle{CVfooter}

\noindent \textbf{\uppercase{Resumé}}
\vspace{2mm}

\noindent \textbf{Thanh Dat Vu}
\vspace{1mm}

\noindent\begin{tabular*}{\textwidth}{@{\extracolsep{\fill}}l r}
Research Scientist & Email: \href{mailto:stephen.t.vu@hotmai.com}{stephen.t.vu@hotmail.com} \\
FPT University & Web: \href{https://datvuthanh.github.io/}{https://datvuthanh.github.io} \\
Hoa Lac, Hanoi & Phone: 866-010-398 \\
\hline
\end{tabular*}

\section{Education \& Training}

\begin{tabular}{l l l l}
FPT University & Hoa Lac, Hanoi & Computer Science & B.Sc, 2018-2021 \\
\end{tabular}

\section{Research \& Professional Experience}

\begin{tabular}{l l}
2018 -- 2019 & Chairman of FPTU Artificial Intelligence Club \\
2017 -- 2018 & Research Intern, Viettel Cyberspace Center \\
\end{tabular}

\section{Research Area}
Stereo matching, stereo image processing, cameras,compensation, correlation methods, semantic segmentation, deep generative models.

\section{Publications}

\vspace{2mm}
\noindent \textbf{\textit{\ \ Most closely related}}
\begin{bibunit}
\nocite{apsrev42Control}
\nocite{datvu2021}
\putbib[publications]
\end{bibunit}
% \vspace{2mm}
% \noindent \textbf{\textit{\ \ Honors \& Awards}}
% \newbibstartnumber{6}
% \begin{bibunit}
% \nocite{apsrev42Control}
% \nocite{CominScience2014,ZeljkovicNanoLetters2014,SoumyanarayananPNAS2013,ZeljkovicScience2012,HoffmanScience2002qpi}
% \putbib[publications]
% \end{bibunit}

\section{Synergistic Activities}
\begin{enumerate}
    \item Working with \href{https://ieeexplore.ieee.org/author/38542826300}{Ph.D. Vinh Quang Dinh} in cover topics such as stereo matching, semantic segmentation, deep generative models:
        \begin{itemize}
            \item Research about creating the corresponding patch in stereo matching by implementing deep generative models as DCGAN combine WGAN or Pix2Pix. There is a part of the plan to write my paper.
            \item Working with Assistant Professor \href{https://scholar.google.com/citations?user=Ei00xroAAAAJ&hl=en}{Hae-Gon Jeon} and Ph.D. Vinh Quang Dinh to improve the result disparity maps (post-processing) in SPIMNET architecture by using Semi-Global Matching, Cross-Scale Cost Aggregation, etc.
        \end{itemize}
    \item Chairman \& Founder in FPTU Artifical Intelligence Club, 2018-2019:
        \begin{itemize}
        \item Manage, and build an artificial intelligence research club. These include developing club culture, communication, and focusing on computer vision issues.
        \item Build a movement and promote AI researching at FPT University. Collaborate with other clubs as well as open talkshows about AI with experts.
        \item Open mini courses to teach member's club about machine learning/ deep learning on supervised learning, unsupervised learning problems.
        \end{itemize}
    \item Research intern in Viettel Cyberspace Center about Speech Recognition, 2017-2018:
        \begin{itemize}
        \item Research about automatic speech recognition based on deep learning method, the traditional method like Hidden Markov Models.
        \item Learn how the voice recognition system works.
        \item Build ASR model based on Connectionist Temporal Classification (CTC) - Deep Speech.
        \item Expert in handling tasks on Linux using Shell script
        \end{itemize}
\end{enumerate}

\section{Honors \& Awards}
\begin{enumerate}

\item Ph.D candidate of UET university (full scholarship) , 2020.

\item The champion of \href{https://www.youtube.com/watch?v=nrzcqZVYOZE&t=194s}{Digital Race}, 2020. \\
    Goodgame is the champion of Digital Race; we won \$42,000.

\item \href{https://drive.google.com/file/d/1iXKCnAM39T3kItMZ2s3miEiHPQIM86nM/view?usp=sharing}{VEF Academy certificate} about Machine Learning, 2019.

\item Nhan Tai Dat Viet, 2016
\item 3rd prize ISEF Vietnam, 2015

\end{enumerate}

\end{document}

